\chapter{Bibliography}

\begin{itemize}
\item
\emph{Mathematical methods for physicists}, G. Arfen, H. Weber, Harcourt Academic Press, 7th edition, 2012.
\item
\emph{Mathematical methods in the physical sciences}, M. Boas, John Wiley, 3rd edition, 2006.
\item
\emph{Complex variables and applications}, J. Brown, R. Churchill, McGraw-Hill, 9th edition, 2012.
\item
\emph{Mathematical methods for optical physics and engineering}, G. Gbur, Cambridge University Press, 2011.
\item
\emph{A first course in complex analysis}, M. Beck, G. Marchesi, D. Pixton, L. Sabalka, version 1.54. 2018.
\item
\emph{Functions of a complex variable}, R. Friedman, Columbia university.
\item
\emph{Fundamentals of photonics}, B. Saleh, M. Teich, John Wiley, 1991.
\item
\emph{Finite elements for electrical engineers}, P. Silvester, R. Ferrari, Cambridge University Press, 3rd edition, 1996.
\item
\emph{Finite difference computing with exponential decay models}, H. Langtangen, Lecture Notes in Computational Science and Engineering, Springer, 2016.
\item
\emph{Introduction to Numerical Methods for Variational Problems}, H. Langtangen, K.-A. Mardal, 2015.
\item
\emph{Finite differences and finite elements: getting to know you}, D. O'Leary, Computing in Science and Engineering, July 2005.
\item
\emph{Waves and fields in inhomogeneous media}, W. Chew, Van Nostrand Reinhold, 1990.
\item
\emph{Numerical techniques for micrometer and millimeter-wave passive structures}, T. Itoh (ed.), John Wiley, 1989.
\item
\emph{Photonic crystals: molding the flow of light}, R. Meade, J. Joannopoulos, J. Winn, Princeton University Press, 1995. 
\item
\emph{Chaos: an introduction to dynamical systems}, K. Alligood, T. Sauer, J. Yorke, Springer, 3rd edition, 2000.
%\item
%\emph{Digital communications: fundamentals and applications}, B. Sklar, Prentice--Hall, 1988.
\end{itemize}
